How Unprecedented Was the February 2021 Texas Cold Snap?

### 2021-12-06 doc/agu21/at-a-glance.tex
Some clarification and wording changes

\begin{block}{Human Impacts}
    \begin{itemize}
        \item Electricity demand would have surpassed the all-season record had generation kept up \cite{ercotpublic_outagesv1:2021}
        \item Over \SI{30000}{\mega\watt} of lost output (mostly natural gas; \cite{busby_cascadingrisks:2021}) in TX for $> \SI{2}{days}$
        \item Grid within minutes of catastrophic failure (\cref{fig:ercot-frequency})
        \item Over 100 people died \cite{mulcahy_urideath:2021}
        \item Estimated \$130 billion damages \cite{busby_cascadingrisks:2021}
        \item Electricity outages caused cascading failures of water supply and other critical infrastructure
        \item Marginalized communities disproportionately affected \cite{dobbins_blackoutdisparity:2021}
    \end{itemize}
    \begin{framed}
        \begin{figure}
            \centering
            \includegraphics[width=\textwidth]{magness_frequency.pdf}
            \caption{
                As demand spiked and generation failed, the Texas grid came within minutes of catastrophic failure.
                Figure from ERCOT~\cite{magness_review:2021}.
            }
            \label{fig:ercot-frequency}
        \end{figure}
    \end{framed}
\end{block}

>>>>

\begin{block}{Human Impacts}
    \begin{itemize}
        \item Electricity demand would have broken all-season record \cite{ercotpublic_outagesv1:2021}
        \item Over \SI{30000}{\mega\watt} of lost output (mostly natural gas; see ref.~\cite{ercotpublic_outagesv2:2021})
        \item Grid within minutes of catastrophic failure (\cref{fig:ercot-frequency})
        \item Over 100 people died \cite{mulcahy_urideath:2021}
        \item Estimated \$130 billion damages \cite{busby_cascadingrisks:2021}
        \item Cascading failures of water supply and other critical infrastructure
        \item Marginalized communities disproportionately affected \cite{dobbins_blackoutdisparity:2021}
    \end{itemize}
    \begin{framed}
        \begin{figure}
            \centering
            \includegraphics[width=0.8\textwidth]{magness_frequency.pdf}
            \caption{
                As demand spiked and generation failed, the Texas grid came within minutes of catastrophic failure.
                Figure from ERCOT~\cite{magness_review:2021}.
            }
            \label{fig:ercot-frequency}
        \end{figure}
    \end{framed}
\end{block}

### 2021-12-06 doc/agu21/how-cold.tex
Some clarification and wording changes

\begin{block}{Historic Cold Snaps}
    Visualizing temperature anomalies facilitates identification of large-scale weather patterns superimposed on long-term climatological averages.
    We compare the February 2021 cold snap (bottom row) to four historic cold snaps.
    \begin{framed}
        \begin{figure}
            \centering
            \includegraphics[width=\textwidth]{historic_events_era5.pdf}
            \caption{
                Anomalies of daily mean temperatures from the ERA-5 reanalysis \cite{hersbach_era5:2020} during previous cold snaps demonstrate a qualitative precedent for severe cold.
            }\label{fig:historic_era5}
        \end{figure}
    \end{framed}
\end{block}

>>>>

\begin{block}{Historic Cold Snaps}
    Visualizing temperature anomalies facilitates identification of large-scale weather patterns superimposed on long-term climatological averages.
    We compare the February 2021 cold snap (bottom row) to four historic cold snaps.
    \begin{framed}
        \begin{figure}
            \centering
            \includegraphics[width=\textwidth, trim = 0.25in 0 0 0.75in, clip]{historic_events_era5.pdf}
            \caption{
                \textbf{Previous cold snaps demonstrate a qualitative precedent for severe cold.}
                Data shows anomalies of daily mean temperatures from the ERA-5 reanalysis \cite{hersbach_era5:2020}.
            }\label{fig:historic_era5}
        \end{figure}
    \end{framed}
\end{block}

### 2021-12-06 doc/agu21/key-findings.tex
Some clarification and wording changes

\begin{block}{Key Insights}
    \begin{enumerate}
        \item Had they occurred today, the December 1989 cold snap would have caused more demand for heating than the February 2021 storm, and several other storms would have caused at least 90\% as much
        \item The Texas grid is designed for summer peak demands, but is highly vulnerable to rare winter freezes
        \item Population growth and electrification necessitate investment in Texas's energy supply; these must be made with system resilience in mind
    \end{enumerate}
\end{block}

>>>>

\begin{block}{Key Insights}
    \begin{enumerate}
        \item Had they occurred today, the December 1989 cold snap would have caused more demand for heating than the February 2021 storm, and several other storms would have caused at least 90\% as much
        \item The Texas grid is designed for summer peaks, but is highly vulnerable to rare winter freezes
        \item Weather at least as cold as that observed during February 2011, which formed and forms the basis for season-ahead preparation \cite{ercotpublic_sarawinter:2020,ercot_sarawinter:2021}, should be expected with probability $\approx$ 1/10
        \item Population growth and electrification necessitate investment in Texas's energy supply; these must consider system resilience
    \end{enumerate}
\end{block}
